Let's Play Congestion Control

### 2017-09-04 tex/paper.tex
Lower training rate to make scenario with multiple senders work. It works now
Improve names in LaTeX formulas; finish algorithm typesetting

The loss function $l_{v_t}$ of the value network is actually the sum of the square of the difference for each of these four moving averages:
\begin{align*}
l_{\text{v}_t} =& \left(R_{\text{packet}_t} - V_\text{packet}(s_t; \theta_\text{v})\right)^2 \\
&+\left(R_{\text{byte}_t} - V_\text{byte}(s_t; \theta_\text{v})\right)^2 \\
&+\left(R_{\text{delay}_t} - V_\text{delay}(s_t; \theta_\text{v})\right)^2 \\
&+\left(R_{\text{duration}_t} - V_\text{duration}(s_t; \theta_\text{v})\right)^2
\end{align*}

@@

With $H$ being the entropy, the actor network minimizes the loss
\begin{align*}
l_{\text{a}_t} =& -\log \left( \pi_W\left( a_t-1 < W \leq a_t \given s_t; \theta_\text{a} \right)\right)\\
&\left( \left(\frac{R_{\text{byte}_t}}{{R_{\text{duration}_t}}} - \frac{v_{\text{byte}_t}}{{v_{\text{duration}_t}}}\right) - \left( \frac{R_{\text{delay}_t}}{{R_{\text{packet}_t}}}- \frac{v_{\text{delay}_t}}{{v_{\text{packet}_t}}} \right)\right)\\ 
&+ \beta H\left(\text{Lognormal}\left( \mu_\text{normal}, {\sigma_{\text{normal}}}^{2}\right) \right).
\end{align*}

@@

\begin{algorithm}
\caption{Partial Action Actor Critic Learning -- pseudocode for each learning thread.}
\label{alg:pal}
\begin{algorithmic}
\Loop
	\State $l_\text{actions} \gets  [] $
	\State $l_\text{states} \gets  [] $
	\State $l_\text{values} \gets  [] $
	\State $l_\text{rewards} \gets  [] $
	\State $l_\text{estimatedValues} \gets  [] $
	\State $l_\text{snapshots} \gets  [] $
	\State $t \gets 0$
	\State $s_0 \gets \text{initialState}()$
	\State $\theta_\text{a} \gets \theta_{\text{a}_\text{g}}$
	\State $\theta_\text{v} \gets \theta_{\text{v}_\text{g}}$
	\Repeat
		\State $l_\text{states}.\text{append}(s_t)$
		\State $l_\text{estimatedValues}.\text{append}(V(s_t; \theta_\text{v}))$
		\If{$t \bmod t_\text{max} = 0$}
			\State $\theta_\text{a} \gets \theta_{\text{a}_\text{g}}$
			\State $\theta_\text{v} \gets \theta_{\text{v}_\text{g}}$
			\State $l_\text{snapshots}.\text{append}((\theta_\text{a}, \theta_\text{v}))$
		\EndIf
		\State Sample $a_t$ from the probability distribution
		\State $l_\text{actions}.\text{append}(a_t)$
		\State $l_{\text{partialActions}_t} \gets \text{partialActions}(a_t)$
		\ForAll{partial actions $a_{\text{p}_{nt}}$ in $l_{\text{partialActions}_t}$}
			\State Take partial action $a_{\text{p}_{nt}}$
		\EndFor
		\State Receive partial reward $r_{\text{p}_{nt'}}$
		\StateIndent[3] where $t' \leq t$ and $0 \leq n \leq\#(l_{\text{partialActions}_{t'}})$
		\If{all partial rewards of $a_{t'}$ were received}
			\State $r_{t'} \gets \text{combination of all partial rewards }r_{\text{p}_{nt'}}$
			\State $l_\text{rewards}.\text{append}(r_{t'})$
			\If{$\#\left(l_\text{rewards}\right) > t_\text{max}$ or the episode is over}
				\State $t_\text{end} = \min\left(t_\text{max}, \#\left( l_\text{rewards} \right)\right)$
				\State $\theta_\text{backup} \gets \left(\theta_\text{a}, \theta_\text{v}\right)$
				\State $\theta_\text{a}, \theta_\text{v} \gets l_\text{snapshots}[0]$
				\State $R_i+1 \gets \frac{l_\text{estimatedValues}[t_\text{end}]}{1-\gamma}]$
				\For{$i\gets t_\text{end}-1, 0$}
					\State $R_i \gets r_i + \gamma r_{i+1}$
					\todo[inline]{Calculate the gradients}
					\State Calculate the gradients $d\theta_\text{a}$ and $d\theta_\text{v}$
					\State $\theta_{\text{a}_\text{g}} \gets \theta_{\text{a}_\text{g}} + d\theta_\text{a}$
					\State $\theta_{\text{v}_\text{g}} \gets \theta_{\text{v}_\text{g}} + d\theta_\text{v}$
				\EndFor
				\State $l_\text{actions} \gets l_\text{actions}[t_\text{max}:] $
				\State $l_\text{states} \gets l_\text{states}[t_\text{max}:] $
				\State $l_\text{values} \gets l_\text{values}[t_\text{max}:] $
				\State $l_\text{rewards} \gets l_\text{rewards}[t_\text{max}:] $
				\State $l_\text{estimatedValues} \gets l_\text{estimatedValues}[t_\text{max}:] $
				\State $l_\text{snapshots} \gets l_\text{snapshots}[1:] $
				\State $\theta_\text{a}, \theta_\text{v} = \theta_\text{backup}$
			\EndIf
		\EndIf
		\State Generate $s_{t+1}$ using $r_{\text{p}_{t'}}$
		\State $t \gets t+1$
	\Until{reaching the end the episode}
\EndLoop
\end{algorithmic}
\end{algorithm}

>>>>

The loss function $l_{v_t}$ of the value network is actually the sum of the square of the difference for each of these four moving averages:
\begin{align*}
l_{\text{v}_t} =& \left(R_{\text{packet},t} - V_\text{packet}(s_t; \theta_\text{v})\right)^2 \\
&+\left(R_{\text{byte},t} - V_\text{byte}(s_t; \theta_\text{v})\right)^2 \\
&+\left(R_{\text{delay},t} - V_\text{delay}(s_t; \theta_\text{v})\right)^2 \\
&+\left(R_{\text{duration},t} - V_\text{duration}(s_t; \theta_\text{v})\right)^2
\end{align*}

@@

With $H$ being the entropy, the actor network minimizes the loss
\begin{align*}
l_{\text{a}_t} =& -\log \left( \pi_W\left( a_t-1 < W \leq a_t \given s_t; \theta_\text{a} \right)\right)\\
&\left( \left(\frac{R_{\text{byte},t}}{{R_{\text{duration},t}}} - \frac{v_{\text{byte},t}}{{v_{\text{duration},t}}}\right) - \left( \frac{R_{\text{delay},t}}{{R_{\text{packet},t}}}- \frac{v_{\text{delay},t}}{{v_{\text{packet},t}}} \right)\right)\\ 
&+ \beta H\left( \pi\left( l_\text{states}[i]; \theta_a \right)\right).
\end{align*}

@@

\begin{algorithm}
\caption{Partial Action Actor Critic Learning -- pseudocode for each learning thread.}
\label{alg:pal}
\begin{algorithmic}[1]
\Loop
	\State $l_\text{actions} \gets  [] $
	\State $l_\text{states} \gets  [] $
	\State $l_\text{values} \gets  [] $
	\State $l_\text{rewards} \gets  [] $
	\State $l_\text{estimatedValues} \gets  [] $
	\State $l_\text{snapshots} \gets  [] $
	\State $t \gets 0$
	\State $s_0 \gets \text{initialState}()$
	\State $\theta_\text{a} \gets \theta_{\text{a},\text{g}}$
	\State $\theta_\text{v} \gets \theta_{\text{v},\text{g}}$
	\Repeat
		\State $l_\text{states}.\text{append}(s_t)$
		\State $l_\text{estimatedValues}.\text{append}(V(s_t; \theta_\text{v}))$
		\If{$t \bmod t_\text{max} = 0$}
			\State $\theta_\text{a} \gets \theta_{\text{a},\text{g}}$
			\State $\theta_\text{v} \gets \theta_{\text{v},\text{g}}$
			\State $l_\text{snapshots}.\text{append}((\theta_\text{a}, \theta_\text{v}))$
		\EndIf
		\State Sample $a_t$ from the probability distribution
		\State $l_\text{actions}.\text{append}(a_t)$
		\State $l_{\text{partialActions},t} \gets \text{partialActions}(a_t)$
		\ForAll{partial actions $a_{{\text{p},n,t}}$ in $l_{\text{partialActions},t}$}
			\State Take partial action $a_{{\text{p},n,t}}$
		\EndFor
		\State Receive partial reward $r_{\text{p},n,t'}$
		\StateIndent[3] where $t' \leq t$ and $0 \leq n \leq\#(l_{\text{partialActions},t'})$
		\If{all partial rewards of $a_{t'}$ were received}
			\State \Call{computeGradients}{}
		\EndIf
		\State Generate $s_{t+1}$ using $r_{\text{p}_{t'}}$
		\State $t \gets t+1$
	\Until{reaching the end the episode}
\EndLoop
%\algstore{palalg}
\end{algorithmic}
\end{algorithm}
\begin{algorithm}
\caption{Partial Action Actor Critic Learning -- procedure which computes and applies the gradients.}
\label{alg:grad}
\begin{algorithmic}[1]%
%\algrestore{palalg}
\Function{computeGradients}{}
	\State $r_{t'} \gets \text{combination of all partial rewards }r_{\text{p},n,t'}$
	\State $l_\text{rewards}.\text{append}(r_{t'})$
	\If{$\#\left(l_\text{rewards}\right) > t_\text{max}$ or the episode is over}
		\State $t_\text{end} = \min\left(t_\text{max}, \#\left( l_\text{rewards} \right)\right)$
		\State $\theta_\text{backup} \gets \left(\theta_\text{a}, \theta_\text{v}\right)$
		\State $\theta_\text{a}, \theta_\text{v} \gets l_\text{snapshots}[0]$
		\State $R_{i+1} \gets \frac{l_\text{estimatedValues}[t_\text{end}]}{1-\gamma}$
		\For{$i\gets t_\text{end}-1, 0$}
			\State $R_i \gets r_i + \gamma r_{i+1}$
			\State $a \gets l_\text{actions}[i]$
			\State $s \gets l_\text{states}[i]$
			\State $v \gets l_\text{values}[i]$
			\State $d\theta_\text{v} \gets \frac{\partial\left(R_i - l_\text{values}[i]\right)}{\partial\theta_v}$
			\State $d\theta_\text{v} \gets -\frac{\partial\log \left( \pi_W\left( a-1 < W \leq a \given s; \theta_\text{a} \right)\right)\left(R_i - v\right)}{\partial\theta_a}$
			\StateIndent[6] $-\frac{\partial\beta H\left( \pi\left( l_\text{states}[i]; \theta_a \right)\right)}{\partial\theta_a}$
			\State $\theta_{\text{a},\text{g}} \gets \theta_{\text{a},\text{g}} + d\theta_\text{a}$
			\State $\theta_{\text{v},\text{g}} \gets \theta_{\text{v},\text{g}} + d\theta_\text{v}$
		\EndFor
		\State $l_\text{actions} \gets l_\text{actions}[t_\text{max}:] $
		\State $l_\text{states} \gets l_\text{states}[t_\text{max}:] $
		\State $l_\text{values} \gets l_\text{values}[t_\text{max}:] $
		\State $l_\text{rewards} \gets l_\text{rewards}[t_\text{max}:] $
		\State $l_\text{estimatedValues} \gets l_\text{estimatedValues}[t_\text{max}:] $
		\State $l_\text{snapshots} \gets l_\text{snapshots}[1:] $
		\State $\theta_\text{a}, \theta_\text{v} = \theta_\text{backup}$
	\EndIf
\EndFunction
\end{algorithmic}
\end{algorithm}
